### 2017-02-06 2017mergingmerges/section/XX-Fusion.tex
just citations

Figure~\ref{fig:Fusion:Def:Top} contains the definitions of top-level fusion functions to fuse a network and a pair of processes.
\ti{fuseNetwork} takes a process network and repeatedly fuses pairs together until all processes in the network have been fused into a single process.
The order processes are fused can affect whether fusion succeeds or fails, so all permutations are tried.
We address this in more detail in~\S\ref{s:FusionOrder}.

\ti{fusePair} fuses a pair of processes together, constructing a new process that computes the outputs of both.
The blocks are constructed by computing a fixpoint, starting at the initial labels of each process with empty input states.
Each block is computed with \ti{tryStepPair}, which statically chooses one of the two processes to execute, and any reachable blocks are added recursively until fixpoint is reached.
This implementation assumes the heap variables are distinct, which can easily be ensured by renaming.

@@

The \ti{tryStepPair} function defined in figure~\ref{fig:Fusion:Def:StepPair} calls this for both processes, and if either machine can execute it will execute that process.
It takes the channel state map, and for both input processes the label with static input state, as well as the instruction at that label.

>>>>

Figure~\ref{fig:Fusion:Def:Top} contains the definitions of top-level fusion functions to fuse a network and a pair of processes.
Function \ti{fuseNetwork} takes a process network and repeatedly fuses pairs together until all processes in the network have been fused into a single process.
The order processes are fused can affect whether fusion succeeds or fails, so all permutations are tried.
We address this in more detail in~\S\ref{s:FusionOrder}.

Function \ti{fusePair} fuses a pair of processes together, constructing a new process that computes the outputs of both.
The blocks are constructed by computing a fixpoint, starting at the initial labels of each process with empty input states.
Each block is computed with \ti{tryStepPair}, which statically chooses one of the two processes to execute, and any reachable blocks are added recursively until fixpoint is reached.
This implementation assumes the heap variables are distinct, which can easily be ensured by renaming.

@@

Function \ti{tryStepPair} defined in figure~\ref{fig:Fusion:Def:StepPair} calls this for both processes, and if either machine can execute it will execute that process.
It takes the channel state map, and for both input processes the label with static input state, as well as the instruction at that label.

### 2017-02-06 2017mergingmerges/section/XX-Related.tex
just citations

>>>>

The duality between pull and push arrays has also been explored in Obsidian by \citep{claessen2012expressive} and later in \citep{svensson2014defunctionalizing}, by explicitly separating the types of pull and push arrays.
Here the distinction is made for the purpose of code generation for GPUs rather than fusion, as operations like append on pull arrays require conditionals inside the loop, whereas using push arrays moves these conditionals outside the loop.
% Here push arrays are `defunctionalized' and represented as a datatype containing the combinator and its arguments, which allows specialised and efficient code generation.
% However this work only supports a limited number of baked-in push combinators such as append, mapping, interleaving and reversing.

Streaming IO libraries have blossomed in the Haskell ecosystem, generally based on Iteratees \cite{kiselyov2012iteratees}.
Libraries such as @conduit@ \cite{hackage:conduit}, @enumerator@ \cite{hackage:enumerator}, @machines@ \cite{hackage:machines} and @pipes@ \cite{hackage:pipes} are all designed to write stream computations with bounded buffers.
However, these libraries are not designed for absolute performance and programs tend to be written to operate over streams of chunks rather than streams of values.
For the most part they support only simple straight-line computations.
